Analysing Constraint Grammars with a SAT-solver

### 2016-02-29 paper/lrec/lrec2016_listenmaa_claessen.tex
right path for cg.bib
small changes to abstract

\abstract{
We describe a method for analysing Constraint Grammars by encoding the
rules in SAT.
Our tools can detect internal conflicts or redundancies in a grammar,
as well as generate examples to demonstrate the effect of some rule or
rule set.
This can help users to diagnose and improve their grammars.
No corpus is required, only a morphological lexicon. \\ 
\newline 
\Keywords{Constrain Grammar, SAT, Grammar Analysis} }

@@

\bibliographystyle{lrec2016}
\bibliography{cg}

>>>>

\abstract{
We describe a method for analysing and improving Constraint Grammars (CG).
% by encoding the rules in SAT.
Traditional CG engines execute the rules in an imperative and
sequential manner, which makes it impossible to track interaction
between rules.
In contrast, we represent CG rules as logic constraints, which
can then be tested for contradictions and inconsistencies.
Our tool can detect internal conflicts or redundancies in a grammar,
as well as generate examples to demonstrate the effect of some rule or
rule set.
This can help users to diagnose and improve their grammars.
No corpus is required, only a morphological lexicon. \\ 
\newline 
\Keywords{Constrain Grammar, SAT, Grammar Analysis} }

@@

\bibliographystyle{lrec2016}
\bibliography{../cg}
